---
title: "FA20 Travel Campaign Quarterly Ad Analytics Project: FY20 Q3"
author: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  pdf_document:
fontsize: 11pt
mainfont: Calibri
sansfont: Calibri
monofont: Calibri
geometry: margin=1in
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r include=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)
library(tinytex)
library(hms)
library(lubridate)
library(stringr)
library(tidyr)
```


```{r, include=FALSE}
options(tinytex.verbose = TRUE)
options(knitr.table.format = "latex")
```

### Brief Description

Marketing is currently in the middle of its Spring Travel Campaign and will be running ads through May, 2020. Traditionally, Marketing has deployed these ads out-of-state,  geo-targeting high school students where USM Admissions' Counselors host various events. In a turn of circumstances, fairs and visits were all cancelled due to the COVID-19 pandemic.  The ads, which promote the University's RSP program, and not any specific events, have been live nonetheless and driving an impressive number of unique pageviews to the campaign landing page. 


```{r}
NewData <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/FlowchartTravel.csv", header = T, stringsAsFactors = F)
```

## Findings



```{r}



NewDataFY19Q3 <- NewData %>% filter(Quarter == "FY20Q3") %>%  separate(Vendor, c("Vendor", "Medium")) %>% 
  select(Medium, Vendor, Quarter, Impressions:End_Date) %>% arrange(Medium, Vendor)

color.me <- which(NewDataFY19Q3$CTR == "0.18%")
#NewDataFY19Q3 <- NewDataFY19Q3[,c(4:13)]
landscape(knitr::kable(NewDataFY19Q3, "latex",caption = "FY20 Q3 Graduate Campaign Targeting All Audiences", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 1) %>%
  pack_rows("Video", 2, 3) 
# %>%
#   row_spec(color.me, bold = T, color = "red", background = "white")
```

```{r}

```

### Conclusions

* The Spring Travel Campaign consists of Programmatic display, and Facebook (FB) and Snapchat (SC)video ads, in contrast to that of last fall which also ran social display ads. 

* Programmatic display and Snapchat video ads performed well. Their CTRs are above benchmarks and they drive a great deal of traffic to the campaign landing page. Performance midway through the campaign has surpassed that of last Fall's entire campaign. 
* Although we do not have benchmarks for Facebook video ads, view-rates have remained consistent and view-through-rates have improved from the Fall Travel Campaign.

* Limiting the FB to video does not appear to have a negative impact on ad driven web traffic.

* This campaign runs through May.




```{r}
NewDataFY19Q3 <- NewData %>% filter(Quarter == "FY19Q3" )%>%  separate(Vendor, c("Vendor", "Medium")) %>% select(Medium, Vendor, Quarter, Impressions:End_Date) %>% arrange(Medium, Vendor)
#NewDataFY19Q3 <- NewDataFY19Q3[,c(4:12)]
landscape(kable(NewDataFY19Q3, "latex", caption = "FY19 Q3 Travel Campaign for a High School Students", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Carousel", 1, 2)%>%
  pack_rows("Display", 3, 5)%>%
  pack_rows("Video", 6, 7)
```


* Out-of-State HS students are being targeted in promotion of the undergraduate degree program. 

```{r}


# __Graduate Degree__
# NewDataFY19Q3 <- NewData %>% filter(Quarter == "FY20Q3" & str_detect(AdSet,"GR" ))
# NewDataFY19Q3 <- NewDataFY19Q3[,c(4:12)]
# landscape(kable(NewDataFY19Q3, "latex", caption = "FY20 Q3 Working Adult Campaign", booktabs = T))%>%
# kable_styling(full_width = T)  
#%>%
  #row_spec(0, angle = -45)
```

```{r eval=FALSE, include=FALSE}
mtcars[1:10, 1:2] %>%
  mutate(
    car = row.names(.),
    mpg = cell_spec(mpg, "latex", color = ifelse(mpg > 20, "red", "blue")),
    cyl = cell_spec(cyl, "latex", color = "white", align = "c", angle = 45, 
                    background = factor(cyl, c(4, 6, 8), 
                                        c("#666666", "#999999", "#BBBBBB")))
  ) %>%
  select(car, mpg, cyl) %>%
  kable(format = "latex", escape = F) %>%
  kable_styling(full_width = F)
```

```{r eval=FALSE, include=FALSE}
NewDataFY19Q3[1:7, 1:11] %>%
  mutate(Vendor = Vendor, 
         Medium = Medium,
    CTR = cell_spec(CTR, "latex", color = ifelse(CTR == "0.34%", "red", "black")),
    UPV = cell_spec(UPV, "latex", color = "white", align = "c", angle = 45, 
                    background = factor(UPV, c("80", "43", "465","199", "96", "229", "80"), 
                                        c("#666666", "#999999", "#BBBBBB","#666666", "#999999", "#BBBBBB","#666666"))), 
    Cost = cell_spec(Cost, "latex", color = ifelse(Cost == "$ 2842.45", "red", "black"))
    
  ) %>%
  select(Medium, Vendor,CTR, UPV,Cost) %>%
  kable(format = "latex", escape = F) %>%
  kable_styling(full_width = F)%>%
  row_spec(0, angle = -45) %>%
  pack_rows("Carousel", 1, 2)%>%
  pack_rows("Display", 3, 5)%>%
  pack_rows("Video", 6, 7)
```

```{r eval=FALSE, include=FALSE}
NewDataFY19Q3[1:7, 1:11] %>%
  mutate(
    CTR = cell_spec(CTR, "latex", color = ifelse(CTR == "0.34%", "red", "black"))) %>%
  kable(format = "latex", escape = FALSE) %>%
  kable_styling("striped", full_width = F)
```