---
title: "FA20 Travel Campaign Quarterly Ad Analytics Project: FY20 Q4"
author: "Office of Marketing and Brand Management"
date: "7/20/2020"
output:
  pdf_document:
fontsize: 11pt
mainfont: Calibri
sansfont: Calibri
monofont: Calibri
geometry: margin=1in
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)
library(tinytex)
library(hms)
library(lubridate)
library(stringr)
library(tidyr)
```


```{r message=FALSE, warning=FALSE, include=FALSE}
options(tinytex.verbose = TRUE)
```

### Brief Description:

Our FY20 Q4 digital campaign promoting the University's Undergraduate program to out-of-state High School students and their influencers consists of a large variety of media platforms. New ad creative and landing pages were rolled out on ____. It is difficult to speculate as to how Covid-19 may have impacted campaign performance, nevertheless, it is important to note that the social distancing due to the global pandemic became mandatory for the entire third month of the quarter. 


```{r echo=FALSE, message=FALSE, warning=FALSE}
NewData1 <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/Flowchart.csv", header = T, stringsAsFactors = F)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
HS_NewDataFY20 <-  NewData1 %>% filter(Quarter == "FY20Q4" & str_detect(AdSet, "TL")) %>%  
  separate(Vendor, c("Vendor", "Medium")) %>% 
  arrange(Medium, Vendor)
HS_NewDataFY20 <- HS_NewDataFY20 %>%  select(Vendor, Impressions:Start_Date) 

landscape(knitr::kable(HS_NewDataFY20, "latex", caption = "Out-of_State High School Student Audience FY20 Q4 Campaign Review: Undergraduate Degree", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 1) %>%
  pack_rows("Video", 2, 3)
  
```







```{r echo=FALSE, message=FALSE, warning=FALSE}
Forms <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/ThankYouFormCompletions.csv", header = T, stringsAsFactors = F)



DCForms <- Forms %>% filter(
  Primary.State.Province != "Maine" & str_detect(Initial.Referral.Source,"HS")) %>% 
  mutate(Date = as.Date(Initial.Source.Date, format = "%m/%d/%Y"),
         LandingPage = 
           ifelse(Date <= "2019-08-01","/everyone",
                  ifelse(Date > "2019-08-01" & Date < "2020-02-18", "/here", "/excel")),
         FY = ifelse(Date < "2019-07-01", "FY19","FY20"), 
         Quarter = paste0((FY),"Q",quarter(Date, with_year = FALSE, fiscal_start = 7))
    
  ) %>% select(FY, Quarter,Date, everything())

DCForms <- DCForms %>% filter(str_detect(Initial.Referral.Source, "HS"), str_detect(Quarter, "4"))
kable(DCForms %>%  
        group_by(FY, Quarter) %>% 
        summarise(`Total Inquiries this Quarter` = n()))
```

Conclusions:

* __Programmatic Display__:  



* __Facebook Video:__ 


* __Snapchat Video:__ 



