---
title: "Marketing Report"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output: 
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(dplyr)
library(knitr)
library(kableExtra)
library(tinytex)
library(hms)
library(lubridate)
library(tufte)
```



```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# Description


Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here. In general,
    \href{https://blog.adstage.io/facebook-ads-benchmarks}{{\color{blue}{\underline{FB Newsfeed }}}} CTR overall experienced a 24% drop from July, 2017 - July, 2018.




# Findings

```{r data 1}
FMOrig <- read.csv("file:///Z:/DAA/Marketing/MKT_output.csv", header = T, stringsAsFactors = F)
```



```{r}
FM <- FMOrig %>% filter(Master_Adname_Type == "NC" )
FM <- FM %>%
   filter(Code_Product == "UG") %>% 
  mutate(
    Code_Audience = ifelse(Master_Adname == "FA20_BR_FB_VID__TL_UG_D_1", "TL", Code_Audience), 
         Code_Product = ifelse(Master_Adname == "FA20_BR_FB_VID__TL_UG_D_1", "UG", Code_Product), 
    
    
    ) %>%
  select(1:8, 13, 15:19, 21:24, 26, 28:29, 31:39, 41) %>% 
  select(Master_Date, everything())

FM <- FM %>% 
  mutate_at(10:31, ~replace(., is.na(.), 0)) %>% 
  mutate(Master_Date = as.Date(Master_Date, format = "%Y-%m-%d"), 
         Master_Results = as.numeric(Master_Results), 
         Master_Engagements = as.numeric(Master_Engagements)) %>% 
  arrange(Master_Date) 

Start <- FM %>% 
  mutate(AdSet = paste0(Code_RecruitingPeriod, "_",Code_Product, "_",Code_Audience, "_",Code_Vendor, "_",Code_Medium, "_",Code_Objective)) %>% 
  group_by(AdSet) %>% summarise(Start_Date = min(Master_Date), End_Date = max(Master_Date))


```


```{r}
FM <- FM %>%
  #filter(Master_Date != "") %>% 
   mutate(FY = ifelse(Master_Date > "2018-06-30 " & Master_Date <= "2019-06-30", "FY19",
                             ifelse(Master_Date >= "2019-07-01 " & Master_Date < "2020-07-01", "FY20","N/A")), 
          AdSet = paste0(Code_RecruitingPeriod, "_",Code_Product, "_",Code_Audience, "_",Code_Vendor, "_",Code_Medium, "_",Code_Objective), 
          Ad = paste0(Code_Audience, "_",Code_Vendor, "_",Code_Medium), 
          Vendor = paste0(Code_Vendor, "_",Code_Medium))

```

```{r}
FMQ19 <- FM%>% 
  mutate(
    Quarter = paste0((FY),"Q",quarter(Master_Date, with_year = FALSE, fiscal_start = 7)), 
    #Vendor_Medium = paste0(Code_Medium, "_", Code_Vendor),
    # Week = (cut(Master_Date + 1, "week")),
    # Week = as.Date(Week, format = "%Y-%m-%d"), 
    ) %>% 
  group_by(Quarter, AdSet, Ad, Vendor) %>% 
  summarise(
    Cost = sum(Master_Cost),
    Clicks = sum(Master_Clicks), 
    Impressions = round(sum(Master_Impressions),0), 
    ClicksToSite = sum(Master_Clicks_To_Site),
    #CTR = paste0(round(Clicks/Impressions * 100, 2), "%"), 
    Bounces = sum(Master_Bounces),
    Sessions = sum(Master_Sessions), 
    UPV = sum(Master_Unique_Pageviews), 
    Views = sum(Master_Views), 
    Completions = sum(Master_Completions), 
    #BounceRate = paste0(round(Bounces/Sessions * 100, 2), "%"), 
    Step1 = sum(Master_Time_On_Page)/(sum(Master_Pageviews)- sum(Master_Exits)), 
    Av_TOP = round_hms(as_hms(Step1), 5), 
    ClickRatePct = round(Clicks/Impressions * 100, 2), 
    BounceRatePct = round(Bounces/Sessions * 100, 2), 
    ViewRate = round(Views/Impressions * 100, 2), 
    VTR = round(Completions/Impressions *100, 2), 
    ClickableCompletions = sum(Master_Clickable_Completions), 
    ClickableCompRate = round(Clicks/ClickableCompletions * 100, 2), 
    Swipes = sum(Master_Swipes), 
    Opens = sum(Master_Clicks_To_Site), 
    Sends = sum(Master_Sends), 
    Engagements = sum(Master_Engagements), 
    Results = sum(Master_Results))





```







```{r data 3}

colorP <- c("#F6A704", "#0E1033","#4E7B14","#A92007","#D47E0A")
 FMVM <- FMQ19  %>% 
   # mutate(
   #   Product_Audience = paste0(Code_Product, "_", Code_Audience)
   #   
   #   ) %>%
   group_by(Quarter,AdSet, Ad, Vendor) %>%
   summarise(
     Cost = round(sum(Cost), 2),
     Clicks = sum(Clicks),
     Impressions = round(sum(Impressions),0),
     #CTR = paste0(round(Clicks/Impressions * 100, 2), "%"),
     Bounces = sum(Bounces),
     Sessions = sum(Sessions),
     UPV = sum(UPV),
     Views = sum(Views),
     Completions = sum(Completions),
     Step1 = sum(Step1),


     #Av_TOP = round_hms(as_hms(Step1), 5),
     ClickRatePct = round(Clicks/Impressions * 100, 2),
     BounceRatePct = round(Bounces/Sessions * 100, 2),
     ViewRate = round(Views/Impressions * 100, 2),
     VTR = round(Completions/Impressions *100, 2),
     ClickableCompletions = sum(ClickableCompletions),
     ClickableCompRate = round(Clicks/ClickableCompletions * 100, 2), 
     Swipes = sum(Swipes), 
     SwipeUpRatePct = round(Swipes/Impressions * 100, 2),
     Opens = sum(Opens),
     CTOR = round(Opens/Clicks * 100, 2), 
     Sends = sum(Sends), 
     LIOpens = sum(Opens),
     #LIClicks = sum(Master_Clicks_Sponsored_InMail),
     OpenRate = round(LIOpens/Sends * 100, 2), 
     Engagements = sum(Engagements),
     Results = sum(Results), 
     EngagementRate = round(Engagements/Impressions * 100, 2),
     EngRate = round((sum(LIOpens)+sum(Engagements))/sum(Sends)*100, 2), 
     Avg_RR = round(sum(Results)/sum(Impressions) * 100, 2)) %>%
   select(Quarter, AdSet,Ad,Vendor,Impressions, Clicks, Bounces, Sessions, Swipes, ClickRatePct, SwipeUpRatePct, UPV, BounceRatePct, #Av_TOP, 
          VTR, CTOR,OpenRate, Sends, ViewRate, ClickableCompletions, Completions, Opens, LIOpens,  Engagements,  EngRate, EngagementRate,   Step1, Cost, Avg_RR, Results) 
 
NewData <- full_join(FMVM, Start) 
```


```{r Hold this}
NewData <- NewData %>%
        mutate(ClickThruRate = paste0(ClickRatePct, "%"),
               BounceRate = paste0(BounceRatePct, "%"),
               Impressions = format(as.numeric(Impressions), big.mark=","), 
               UPV = format(as.numeric(UPV),  big.mark="," ),
               Av_TOP = round_hms(as_hms(Step1), 5), 
               Start_Date = format(as.Date(Start_Date), "%m-%y"), 
               End_Date = format(as.Date(End_Date), "%m-%y")
                 
                 #format(as.Date(dates), "%Y-%m")
                 ) %>%
         select(Quarter, AdSet, Ad,Vendor,Impressions, CTR = ClickThruRate, UPV, BR = BounceRate, Av_TOP, Cost, Start_Date, End_Date) %>% filter(Impressions > 0)

kable(NewData)
```


```{r}

```

## FY19 Q1 Undergraduate Program


```{r}
library(stringr)
NewDataFY19Q1 <- NewData %>% filter(Quarter == "FY19Q1" & str_detect(Ad, "HS"))
NewDataFY19Q1 <- NewDataFY19Q1[,c(4:11)]
knitr::kable(NewDataFY19Q1, "latex", caption = "FY19 Q1 Campaign to HS Students", booktabs = T)%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -75)
```


```{r}

NewDataFY19Q1 <- NewData %>% filter(Quarter == "FY19Q1" & str_detect(Ad, "TL"))
NewDataFY19Q1 <- NewDataFY19Q1[,c(4:11)]
knitr::kable(NewDataFY19Q1, "latex", caption = "FY19 Q1 Campaign to Out-of-State HS Students", booktabs = T)%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -75)

```

```{r}

NewDataFY19Q1 <- NewData %>% filter(Quarter == "FY19Q1" & str_detect(Ad, "IN"))
NewDataFY19Q1 <- NewDataFY19Q1[,c(4:11)]
knitr::kable(NewDataFY19Q1, "latex", caption = "FY19 Q1 Campaign to Influencers", booktabs = T)%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -75)
```

```{r eval=FALSE, include=FALSE}

kable(NewData %>% filter(Quarter == "FY19Q1") %>% select(Ad:Cost), "latex", caption = " Total Inquiries by Contract Period", booktabs = T) %>%
kable_styling(full_width = NULL)  %>%
  row_spec(0, angle = -45)
# %>%
# pack_rows(index=c("Contract 2016 - 2017 " = 2, "Contract 2017 - 2018" = 2, "Contract 2018 - 2019" = 2, "Contract 2019 - 2020" = 2))
```

## FY19 Q2

```{r eval=FALSE, include=FALSE}
knitr::kable(
  NewData%>% filter(Quarter == "FY19Q2") %>% select(AdSet, Impressions, CTR, UPV, BR, Av_TOP, Cost,Start_Date, End_Date)
) 
```

## FY19 Q3

```{r eval=FALSE, include=FALSE}


knitr::kable(
  NewData  %>% filter(Quarter == "FY19Q3")%>% select(AdSet, Impressions, CTR, UPV, BR, Av_TOP, Cost))
```

## FY19 Q4

```{r eval=FALSE, include=FALSE}
knitr::kable(
  NewData  %>% filter(Quarter == "FY19Q4")%>% select(AdSet, Impressions, CTR, UPV, BR, Av_TOP, Cost))
```

## FY20 Q1

```{r eval=FALSE, include=FALSE}
knitr::kable(
  NewData %>% filter(Quarter == "FY20Q1")%>% select(AdSet, Impressions, CTR, UPV, BR, Av_TOP, Cost))
```

## FY20 Q2

```{r eval=FALSE, include=FALSE}
knitr::kable(
  NewData %>%  filter(Quarter == "FY20Q2")%>% select(AdSet, Impressions, CTR, UPV, BR, Av_TOP, Cost))
```

## FY20 Q3

```{r eval=FALSE, include=FALSE}
knitr::kable(
  NewData %>%  filter(Quarter == "FY20Q3")%>% select(AdSet, Impressions, CTR, UPV, BR, Av_TOP, Cost))
```




## Plots




## Tables

You can use the `kable()` function from the **knitr** package to format tables that integrate well with the rest of the Tufte handout style. The table captions are placed in the margin like figures in the HTML output.

Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here.
Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here.
Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here.




```{r}
knitr::kable(
  mtcars[1:6, 1:6], caption = 'A subset of mtcars.'
)
```


# Conclusion

* 
* 
* 
