---
title: "FA20 Graduate Campaign Quarterly Ad Analytics Project: FY20 Q3"
author: "Office of Marketing and Brand Management"
date: "3/25/2020"
output:
  pdf_document:
fontsize: 11pt
mainfont: Calibri
sansfont: Calibri
monofont: Calibri
geometry: margin=1in
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r include=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)
library(tinytex)
library(hms)
library(lubridate)
library(tidyr)
library(stringr)
```


```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```


```{r}
NewData <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/FlowchartGrad.csv", header = T, stringsAsFactors = F)
```




### Brief Description:

The FY20 advertising campaign for the University's Graduate program has been multiphasic; part III (using the new creative and landing page) started midway through the 3rd quarter. The Q3 portfolio consists of Programmatic display, Facebook video, and LinkedIn Inbox. Transition from /here to /excel has been seamless. It is difficult to speculate as to how Covid-19 may have impacted campaign performance, nevertheless, it is important to note that the social distancing due to the global pandemic became mandatory for the entire third month of the quarter. 


### Findings


```{r}
NewDataFY19Q3 <- NewData %>% filter(Quarter == "FY20Q3" & str_detect(AdSet, "GR_ALL")) %>%  separate(Vendor, c("Vendor", "Medium")) %>% select(Medium, Vendor, Quarter, Impressions:End_Date) %>% arrange(Medium, Vendor)
#NewDataFY19Q3 <- NewDataFY19Q3[,c(4:13)]
landscape(knitr::kable(NewDataFY19Q3, "latex", caption = "FY20 Q3 Graduate Campaign Targeting All Audiences", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 3) %>%
  pack_rows("Text", 4, 4) %>% 
  pack_rows("Video", 5, 6)
```


```{r}
NewDataFY19Q4 <- NewData %>% 
  filter(Quarter == "FY20Q4" & str_detect(AdSet, "GR_ALL")) %>%  
  separate(Vendor, c("Vendor", "Medium")) %>% 
  select(Medium, Vendor, Quarter, Impressions:End_Date) %>% 
  arrange(Medium, Vendor)
#NewDataFY19Q3 <- NewDataFY19Q3[,c(4:13)]
landscape(knitr::kable(NewDataFY19Q3, "latex", caption = "FY20 Q3 Graduate Campaign Targeting All Audiences", booktabs = T)) %>% 
kable_styling(full_width = T) %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 2) %>%
  pack_rows("Text", 3, 4) 


Campaign <- rbind.data.frame(NewDataFY19Q3, NewDataFY19Q4)
Campaign %>% filter(str_detect(Start_Date, "2020")) %>% arrange(Vendor)
```

```{r}
Forms <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/ThankYouFormCompletions.csv", header = T, stringsAsFactors = F)



DCForms <- Forms %>% filter(str_detect(Initial.Referral.Source,"GR")) %>% 
  mutate(Date = as.Date(Initial.Source.Date, format = "%m/%d/%Y"),
         LandingPage = 
           ifelse(Date <= "2019-08-01","/other",
                  ifelse(Date > "2019-08-01" & Date < "2020-02-18", "/here", "/excel")),
         FY = ifelse(Date < "2019-07-01", "FY19","FY20"), 
         Quarter = paste0((FY),"Q",quarter(Date, with_year = FALSE, fiscal_start = 7))
    
  ) %>% select(FY, Quarter,Date, everything())

DCForms <- DCForms %>% filter(str_detect(Initial.Referral.Source, "GR"), str_detect(Quarter, "3"))
kable(DCForms %>%  
        group_by(FY, Quarter, LandingPage) %>% 
        summarise(`Total Inquiries this Quarter` = n()))
```

### Conclusions:

* Ad driven traffic to the campaign landing page was very strong this quarter 

* __Programmatic Display: __ The overall CTR at  0.1%, meets our expectations and is higher than it was during the previous two phases. The Spring creative has a slightly lower CTR than that of the Fall, and we have seen fewer inquiries since the /excel campaign launch, but I will keep checking into this.

* __Facebook Video:__ Facebook has not published benchmarks for this platform. View and completion rates are \textcolor{red}{slightly down} from this same quarter FY19, but the website has far more unique pageviews.

* __LinkedIn Inbox:__ This platform continues to out-perform the benchmark open-rate.

* __Instagram Display and Video:__ Although only a small portion of the budget is allocated to these platforms, results continue to be positive.

* __Inquiries:__ Form completions for the Graduate program are \textcolor{red}{down} by 50% as displayed above.