---
title: "FA20 Degree Completion Campaign Quarterly Ad Analytics Project: FY20 Q4"
author: "Office of Marketing and Brand Management"
date: "7/15/2020"
output:
  pdf_document:
fontsize: 11pt
mainfont: Calibri
sansfont: Calibri
monofont: Calibri
geometry: margin=1in
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r include=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)
library(tinytex)
library(hms)
library(lubridate)
library(stringr)
library(tidyr)
```


```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

### Brief Description:

Our FY20 Q4 digital campaign promoting the University programs, specifically Degree Completion, to a working adult audience, was successful when measure by web traffic driven by ads; there was nearly a 60% increase in UPV in Q4 from Q3, despite a 30% drop in budget. Additionally, quarterly inquiries are at a 2 year high. The portfolio is made up mostly by display and text ads. A small percentage of the budget goes to video. 


```{r}
NewData1 <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/Flowchart.csv", header = T, stringsAsFactors = F)
```

### Findings

```{r}

WA_NewDataFY20 <-  NewData1 %>% filter(Quarter == "FY20Q4" & str_detect(AdSet, "DC")) %>%  
  separate(Vendor, c("Vendor", "Medium")) %>% 
  arrange(Medium, Vendor)
WA_NewDataFY20 <- WA_NewDataFY20 %>%  select(Vendor:End_Date) %>% arrange(Medium, Vendor)


#NewDataFY19Q3 <- NewDataFY19Q3[,c(4:13)]
landscape(knitr::kable(WA_NewDataFY20, "latex", caption = "FY20 Q4 Campaign Review: Degree Completrion Program for Working Adults", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 3) %>%
  pack_rows("TEXT", 4, 5) %>% 
  pack_rows("Video", 6, 7) 
  
```


__Inquiries__

```{r echo=FALSE}
Forms <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/ThankYouFormCompletions.csv", header = T, stringsAsFactors = F)
DCForms <- Forms %>% filter(str_detect(Initial.Referral.Source,"DC")) %>% 
  mutate(
    Date = as.Date(Initial.Source.Date, format = "%m/%d/%Y"),
    FY = ifelse(Date < "2019-07-01", "FY19","FY20"), 
    Quarter = paste0((FY),"Q",quarter(Date, with_year = FALSE, fiscal_start = 7))
    
  ) %>% select(FY, Quarter,Date, everything())

DCForms <- DCForms %>% filter(str_detect(Initial.Referral.Source, "DC"), str_detect(Quarter, "4"))
kable(DCForms %>%  
        group_by(FY, Quarter) %>% 
        summarise(`Total Inquiries this Quarter` = n()))
```

Conclusions:

* __Programmatic Display__: Q4 CTR dropped slightly from Q3, however it is still higher than the CTR we saw with Programmatic Umbrella ads. BR was also slightly better. 

* __Facebook Display:__  Q4 CTR (0.38%) was dramatically better than Q3's (0.22%). There was also more web traffic, a better bounce rate, and a consistent average time on page  from Q3. 


* __Gmail Text:__ The CTOR, 1.77% \textcolor{red}{is below} the higher education benchmark, however is is slightly higher than Q3. The average time on page and UPV are also higher with a small budget increase. The CTOR should be discussed with Rinck as the benchmark is 6%.
			
* LinkedIn Text:__ 	The CTR continues to be above the national benchmark. The UPV quadrupled while the budget was consistent from last quarter. 

* __Facebook Video:__ While the budget was small this quarter, CTR, VT, VTR, and UPV all increased. 

*	__Inquiries:__ The number of inquiries generated by this campaign has been small over the past 8 quarters, however, as mentioned in the introduction, was currently at a two year high, 11.


\href{https://www.wrike.com/open.htm?id=502328427}{{\color{blue}{\underline{Wrike Project Details}}}}































