---
title: "FA20 Graduate Campaign Quarterly Ad Analytics Project: FY20 Q4"
author: "Office of Marketing and Brand Management"
date: "7/15/2020"
output:
  pdf_document:
fontsize: 11pt
mainfont: Calibri
sansfont: Calibri
monofont: Calibri
geometry: margin=1in
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r include=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)
library(tinytex)
library(hms)
library(lubridate)
library(stringr)
library(tidyr)
```


```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

### Brief Description:

Overall the FY20 Q4 digital campaign promoting the University's Graduate program saw a 72% increase in web traffic on a budget that was 14% smaller. However inquiries dropped to their lowest in nearly 2 years and are 80% lower than they were in FY19Q3, when they were at their apex. (FY19Q4 = 75, FY20Q4 = 15.) Despite this, digital ads performed as hoped. 


```{r}
NewData1 <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/Flowchart.csv", header = T, stringsAsFactors = F)
```


### Findings

```{r}

GR_NewDataFY20 <-  NewData1 %>% filter(Quarter == "FY20Q4" & str_detect(AdSet, "GR")) %>%  
  separate(Vendor, c("Vendor", "Medium")) %>% 
  arrange(Medium, Vendor)
GR_NewDataFY20 <- GR_NewDataFY20 %>%  select(Vendor:End_Date) %>% arrange(Medium, Vendor)


#NewDataFY19Q3 <- NewDataFY19Q3[,c(4:13)]
landscape(knitr::kable(GR_NewDataFY20, "latex", caption = "FY20 Q4 Campaign Review: Graduate Degree Program Degree", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 2) %>%
  pack_rows("Story", 3, 4) 
  
```


Inquiries

```{r }
Forms <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/ThankYouFormCompletions.csv", header = T, stringsAsFactors = F)
DCForms <- Forms %>% filter(str_detect(Initial.Referral.Source,"GR")) %>% 
  mutate(
    Date = as.Date(Initial.Source.Date, format = "%m/%d/%Y"),
    FY = ifelse(Date < "2019-07-01", "FY19","FY20"), 
    Quarter = paste0((FY),"Q",quarter(Date, with_year = FALSE, fiscal_start = 7))
    
  ) %>% select(FY, Quarter,Date, everything())

DCForms <- DCForms %>% filter(str_detect(Initial.Referral.Source, "GR"), str_detect(Quarter, "4"))
kable(DCForms %>%  
        group_by(FY, Quarter) %>% 
        summarise(`Total Inquiries this Quarter` = n()))
```



### Conclusions:

* __Programmatic Display__: The \textcolor{red}{CTR dropped} from 0.1% in Q3 to 0.07% in Q4. Nevertheless, this value is higher than those we saw with Programmatic Umbrella ads. The web traffic dropped by the same amount that the budget did while the BR was better. 
		
* __Instagram Display:__ Q4 CTR increased slightly from Q3. It remains well above benchmark. UPV were also up.
			
			
* __Facebook Video:__ All performance metrics remained steady and the BR was better. The budget was slightly larger.

* __Instagram Video:__ Like FB video, all performance metrics remained steady and the BR was better. 

* __Inquiries:__ As mentioned in the introduction above, inquiries are at a nearly \textcolor{red}{2 year low} . This is inconsistent with the growth in Graduate applications this year. 



\href{https://www.wrike.com/open.htm?id=502328134}{{\color{blue}{\underline{Wrike Project Details}}}}






























