---
title: "FA20 Transfer Campaign Quarterly Ad Analytics Project: FY20 Q3"
author: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  pdf_document:
fontsize: 11pt
mainfont: Calibri
sansfont: Calibri
monofont: Calibri
geometry: margin=1in
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r include=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)
library(tinytex)
library(hms)
library(lubridate)
library(stringr)
library(tidyr)
```


```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r}
#First run data "C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/FlowchartTransfer.csv" 
## Revised data
# "C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/FlowchartTransfer_V2.csv"
```

### Brief Description:

Our digital campaign promoting the University's Transfer program this quarter consists mainly of Programmatic display and Facebook, YouTube, and Snapchat video. The creative was refreshed midway through the quarter.

```{r}
NewData1 <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/FlowchartTransfer.csv", header = T, stringsAsFactors = F)

NewData2 <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/FlowchartTransfer_V2.csv", header = T, stringsAsFactors = F)
```


```{r}
NewDataFY20 <-  NewData2 %>% filter(Quarter == "FY20Q3" & str_detect(AdSet, "TR")) %>%  
  separate(Vendor, c("Vendor", "Medium")) %>% 
  mutate(Start_Date = as.Date(
    Start_Date, format = "%Y-%m-%d"), 
    End_Date = as.Date(End_Date, format = "%Y-%m-%d" )) %>% 
  
  group_by(Medium, Vendor) %>% 
  summarise(
    Clicks = sum(Clicks), 
    Impressions = sum(Impressions), 
    Bounces = sum(Bounces), 
    Sessions = sum(Sessions), 
    UPV = sum(UPV),
    Views = sum(Views),
    Completions = sum(Completions),
    Step1 = sum(Step1),
    ClickRatePct = round(Clicks/Impressions * 100, 2),
    BounceRatePct = round(Bounces/Sessions * 100, 2),
    ViewRate = round(Views/Impressions * 100, 2),
    VTR = round(Completions/Impressions *100, 2),
    Cost = sum(Cost),
    Start_Date_New = min(Start_Date),
    End_Date_New = max(End_Date)
  ) %>% 
  mutate(ClickThruRate = paste0(ClickRatePct, "%"),
         BounceRate = paste0(BounceRatePct, "%"),
         Impressions = format(as.numeric(Impressions), big.mark=","), 
         UPV = format(as.numeric(UPV),  big.mark="," ),
         Cost = paste0("$ ", Cost),
         Av_TOP = round_hms(as_hms(Step1), 5), 
         Start_Date = format(as.Date(Start_Date_New), "%m-%Y"), 
         End_Date = format(as.Date(End_Date_New), "%m-%Y"), 
         End_Date = ifelse(End_Date == format(Sys.Date(),"%m-%Y"), "Ongoing", End_Date)) %>% 
  select(
    Medium, 
    Vendor, 
    Impressions, 
    ClickThruRate, 
    UPV, 
    BounceRate, 
    Av_TOP, 
    Cost,
    Start_Date, 
    End_Date
  )
  
```


```{r}
# NewData2 <- NewData %>% 
#   group_by(Medium, Vendor)
```

### Findings

```{r}
NewDataFY19Q3 <- NewDataFY20 %>%  select(Medium:End_Date) %>% arrange(Medium, Vendor)
#NewDataFY19Q3 <- NewDataFY19Q3[,c(4:13)]
landscape(knitr::kable(NewDataFY19Q3, "latex", caption = "FY20 Q3 Campaign Review: Transfer Degree", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 2) %>%
  pack_rows("Text", 3, 3) %>%
  pack_rows("Video", 4, 7)
  
```




```{r}
Forms <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/ThankYouFormCompletions.csv", header = T, stringsAsFactors = F)

TrForms <- Forms %>% filter(str_detect(Initial.Referral.Source, "TR")) %>% 
  mutate(
    Date = as.Date(Initial.Source.Date, format = "%m/%d/%Y"),
    FY = ifelse(Date < "2019-07-01", "FY19","FY20"), 
    Quarter = paste0((FY),"Q",quarter(Date, with_year = FALSE, fiscal_start = 7))
    
  ) %>% select(FY, Quarter,Date, everything())

TrForms <- TrForms %>% filter(str_detect(Initial.Referral.Source, "TR"), str_detect(Quarter, "3"))
kable(TrForms %>%  
        group_by(FY, Quarter) %>% 
        summarise(`Total Inquiries this Quarter` = n()))
```



```{r}
# NewDataFY19Q3 <- NewData1 %>% 
#   filter(
#     Quarter == "FY20Q3" & str_detect(AdSet, "TR")) %>% 
#   mutate(
#     Vendor = str_sub(AdSet, 12, 14),
#     Vendor = ifelse(str_detect(Vendor, "_"), str_sub(Vendor, 1,2), Vendor),
#     Medium = str_sub(AdSet, 15,18), 
#     Medium = ifelse(str_detect(Medium, "DIS"), "Display", ifelse(str_detect(Medium, "VI"), "Video", "Story"))) %>% select(Medium,Vendor,  Impressions, CTR, UPV, BR, Av_TOP, Cost, Start_Date, End_Date) %>% arrange(Medium, Vendor)
# NewDataFY19Q3 <- NewDataFY19Q3[,c(1:10)]
# landscape(knitr::kable(NewDataFY19Q3, "latex", caption = "FY20 Q3 Transfer Campaign", booktabs = T))%>%
# kable_styling(full_width = T)  %>%
#   row_spec(0, angle = -45) %>%
#   pack_rows("Display", 1, 3) %>%
#   pack_rows("Story", 4,5) %>%
#   pack_rows("Video", 6, 12)
```

```{r}
# NewDataFY20Q <-  NewData2 %>% filter(str_detect(AdSet, "TR")) %>%  
#   separate(Vendor, c("Vendor", "Medium")) %>% 
#   mutate(Start_Date = as.Date(
#     Start_Date, format = "%Y-%m-%d"), 
#     End_Date = as.Date(End_Date, format = "%Y-%m-%d" )) %>% 
#   group_by(Quarter,Medium, Vendor) %>% 
#   summarise(
#     Clicks = sum(Clicks), 
#     Impressions = sum(Impressions), 
#     Bounces = sum(Bounces), 
#     Sessions = sum(Sessions), 
#     UPV = sum(UPV),
#     Views = sum(Views),
#     Completions = sum(Completions),
#     Step1 = sum(Step1),
#     ClickRatePct = round(Clicks/Impressions * 100, 2),
#     BounceRatePct = round(Bounces/Sessions * 100, 2),
#     ViewRate = round(Views/Impressions * 100, 2),
#     VTR = round(Completions/Impressions *100, 2),
#     Cost = sum(Cost),
#     Start_Date_New = min(Start_Date),
#     End_Date_New = max(End_Date)
#   ) %>% 
#   mutate(ClickThruRate = paste0(ClickRatePct, "%"),
#          BounceRate = paste0(BounceRatePct, "%"),
#          Impressions = format(as.numeric(Impressions), big.mark=","), 
  #        UPV = format(as.numeric(UPV),  big.mark="," ),
  #        Cost = paste0("$ ", Cost),
  #        Av_TOP = round_hms(as_hms(Step1), 5), 
  #        Start_Date = format(as.Date(Start_Date_New), "%m-%Y"), 
  #        End_Date = format(as.Date(End_Date_New), "%m-%Y"), 
  #        End_Date = ifelse(End_Date == format(Sys.Date(),"%m-%Y"), "Ongoing", End_Date)) %>% 
  # select(
  #   Medium, 
  #   Vendor, 
  #   Impressions, 
  #   ClickThruRate, 
  #   UPV, 
  #   BounceRate, 
  #   Av_TOP, 
  #   Cost,
  #   Start_Date, 
  #   End_Date
  # )

```


```{r eval=FALSE, include=FALSE}


# NewDataFY19Q3 <- NewDataFY20Q %>% arrange(Quarter,Medium, Vendor) %>%  select(Medium:End_Date) 
# NewDataFY19Q3 <- NewDataFY19Q3[c(15:42),]
# landscape(knitr::kable(NewDataFY19Q3, "latex", caption = "All Quarters: Transfer Degree", booktabs = T)) %>%
# kable_styling(full_width = T)  %>%
#   row_spec(0, angle = -45) %>%
#   # pack_rows("FY19Q1", 1, 4) %>%
#   # pack_rows("FY19Q2", 5, 10) %>%
#   # pack_rows("FY19Q3", 11,14) %>% 
#   pack_rows("FY20Q1", 1,5) %>% 
#   pack_rows("FY20Q2", 6,14) %>%
#   pack_rows("FY20Q3", 15,22) 
#   
  
```

### Conclusions:

* A strong quarter overall.

* __Programmatic Display:__ Performance continues to be strong. The CTR is steady and meets our expectations. The ads are driving traffic with encouraging numbers for the second consecutive quarter.

* __Snapchat Video:__ The CTR is above the national benchmark and as we have seen recently, it drives a great deal of traffic to the campaign landing page with a high bounce rate.

* __YouTube:__ We continue to see view rates above the benchmark. 

* __Instagram Stories:__ We do not have benchmarks for this platform, however since last quarter, which was first time we started differentiating them from IG video, we have seen consistent view rates at 88%  and view-through-rates at 1.0%. 

* __Inquiries:__ We are \textcolor{red}{down}  from 75 inquiries from last year same quarter to 47 this year.



