---
title: "FA20 Undergraduate Campaign Quarterly Ad Analytics Project: FY20 Q4"
author: "Office of Marketing and Brand Management"
date: "7/15/2020"
output:
  pdf_document:
fontsize: 11pt
mainfont: Calibri
sansfont: Calibri
monofont: Calibri
geometry: margin=1in
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r include=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)
library(tinytex)
library(hms)
library(lubridate)
library(stringr)
library(tidyr)
```


```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

### Brief Description:

Our FY20 Q4 digital campaign promoting the University's Undergraduate program to in-state High School students and their influencers consists of a large variety of media platforms. New ad creative and landing pages were rolled out on February 18,2020. Transition from /here to /excel had been smooth in Q3 and. It is important to note that the social distancing due to the global pandemic is still mandatory; this may impact KPI. With the exception of Programmatic display, metrics have been consistent or better than Q3's. Inquiries are down from this time last year.


```{r}
NewData1 <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/Flowchart.csv", header = T, stringsAsFactors = F)
```

# Findings by Audience 


```{r }

HS_NewDataFY20 <-  NewData1 %>% filter(Quarter == "FY20Q4" & str_detect(AdSet, "HS")) %>%  
  separate(Vendor, c("Vendor", "Medium")) %>% 
  arrange(Medium, Vendor)
HS_NewDataFY20 <- HS_NewDataFY20 %>%  select(Vendor:End_Date) %>% arrange(Medium, Vendor)


#NewDataFY19Q3 <- NewDataFY19Q3[,c(4:13)]
landscape(knitr::kable(HS_NewDataFY20, "latex", caption = "High School Student Audience FY20 Q4 Campaign Review: Undergraduate Degree", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 1) %>%
  pack_rows("Story", 2, 2) %>%
  pack_rows("Video", 3, 6)
  
```

```{r}
IN_NewDataFY20 <-  NewData1 %>% filter(Quarter == "FY20Q4" & str_detect(AdSet, "IN")) %>%  
  separate(Vendor, c("Vendor", "Medium")) %>% 
  arrange(Medium, Vendor)

IN_NewDataFY20 <- IN_NewDataFY20 %>%  select(Vendor:End_Date) %>% arrange(Medium, Vendor)

landscape(knitr::kable(IN_NewDataFY20, "latex", caption = "Influencer Audience FY20 Q4 Campaign Review: Undergraduate Degree", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 1) %>%
  pack_rows("Video", 2, 2)
```




```{r eval=FALSE, include=FALSE}
NewDataFY19Q4 <-  NewDataFY19Q4 %>%
  mutate(Vendor = Vendor, 
         Medium = Medium,
         Impressions = Impressions,
    CTR = cell_spec(CTR, "latex", color = ifelse(CTR == "0.38%", "red", "black")),
    UPV = UPV, 
    Cost = cell_spec(Cost, "latex", color = ifelse(Cost == "$ 4939.1", "red", "black"))
    
  ) %>%
  select(Vendor, Impressions,CTR, UPV,Cost)


landscape(kable(NewDataFY19Q3, format = "latex", escape = F, caption =  "FY20 Q4 Undergraduate Campaign Targeting HS Students", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 4) %>%
  pack_rows("Video", 7, 13) %>%
  pack_rows("Instagram Stories", 5, 6) 


  # kable(format = "latex", escape = F, booktabs = T) %>%
  # kable_styling(full_width = T)%>%
  # row_spec(0, angle = -45) %>%
  # pack_rows("Display", 1, 4)%>%
  # pack_rows("IG Stories", 5, 6)%>%
  # pack_rows("Video", 7, 13)
```



Inquiries

```{r eval=FALSE, include=FALSE}
Forms <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/ThankYouFormCompletions.csv", header = T, stringsAsFactors = F)

DCForms <- Forms %>% filter(str_detect(Initial.Referral.Source,"HS")) %>% 
  mutate(
    Date = as.Date(Initial.Source.Date, format = "%m/%d/%Y"),
    FY = ifelse(Date < "2019-07-01", "FY19","FY20"), 
    Quarter = paste0((FY),"Q",quarter(Date, with_year = FALSE, fiscal_start = 7))
    
  ) %>% select(FY, Quarter,Date, everything())

DCForms <- DCForms %>% filter(str_detect(Initial.Referral.Source, "HS"), str_detect(Quarter, "4"))
kable(DCForms %>%  
        group_by(FY, Quarter) %>% 
        summarise(`Total Inquiries this Quarter` = n()))
```


```{r}
Forms <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/ThankYouFormCompletions.csv", header = T, stringsAsFactors = F)



DCForms <- Forms %>% filter(str_detect(Initial.Referral.Source,"HS")) %>% 
  mutate(Date = as.Date(Initial.Source.Date, format = "%m/%d/%Y"),
         LandingPage = 
           ifelse(Date <= "2019-08-01","/everyone",
                  ifelse(Date > "2019-08-01" & Date < "2020-02-18", "/here", "/excel")),
         FY = ifelse(Date < "2019-07-01", "FY19","FY20"), 
         Quarter = paste0((FY),"Q",quarter(Date, with_year = FALSE, fiscal_start = 7))
    
  ) %>% select(FY, Quarter,Date, everything())

DCForms <- DCForms %>% filter(str_detect(Initial.Referral.Source, "HS"), str_detect(Quarter, "4"))
kable(DCForms %>%  
        group_by(FY, Quarter, LandingPage) %>% 
        summarise(`Total Inquiries this Quarter` = n()))
```

Conclusions:

* __Programmatic Display__: This quarter brought a smaller DBM campaign. The \textcolor{red}{CTR dropped} to 0.07% in Q4 from 0.11% in Q3. We haven't seen CTR this low from DBM in FY20. Although we budgeted about 65% less this quarter, CTR should not have been affected. UPV were down 40% from the previous quarter, not as drastically as the budget. 

* __Pinterest Display:__  Pinterest ran through most of this quarter and performed impressively.  The CTR was well above benchmark.
		
* __Instagram Stories:__ Overall, the CTR, UPV, VR, and VTR have performed at the same level as the previous quarter. These metrics have to suffice as performance measures in the absence of benchmarks and are encouraging at this point in time.

* __Instagram Video:__
			
* __Facebook Video:__ We maintained the budget for this platform from the previous quarter and saw twice as many UPV we we saw in the previous quarter. The CTR dropped from 0.42% to 0.33%. However both the VR and VTR went up since last quarter.

* __Instagram Video:__ Like Facebook, we maintained the budget for this platform in 04. The CTR dropped slightly while UPV nearly doubled as well. Both the VR and VTR remained stable.

*	__Pinterest Video:__ Q4 performance is on par with Q3's. 

* __Snapchat Video:__ As anticipated web traffic dropped from last quarter, however we saw an unusual amount in Q3. Nonetheless the CTR went up from Q3. It remains well above benchmark.

* __Youtube Video:__ Performed on par with Q3.Check VR and VTR though Budget doubled. national benchmark of 20%


*	__Pinterest for Influencers:__ Performance in Q4 has been similar to that in Q3.

* __Inquiries:__ For the second quarter in a row, we have seen a significant drop in inquiries from the same quarter in FY19. However, inquiries are up by 4 from FY20 Q3, from 49 to 52.


---

\href{https://www.wrike.com/open.htm?id=502327536}{{\color{blue}{\underline{Wrike Project Details}}}}



























