---
title: "FA20 Working Adult Campaign Quarterly Ad Analytics Project: FY20 Q3"
author: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  pdf_document:
fontsize: 11pt
mainfont: Calibri
sansfont: Calibri
monofont: Calibri
geometry: margin=1in
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r include=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)
library(tinytex)
library(hms)
library(lubridate)
library(stringr)
library(tidyr)
```


```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```


```{r}
NewData <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/FlowchartWorkingAdult_V2.csv", header = T, stringsAsFactors = F)
```




```{r}
NewDataFY20 <-  NewData %>% filter(Quarter == "FY20Q3" & str_detect(AdSet, "WA")) %>%  
  separate(Vendor, c("Vendor", "Medium")) %>% 
  mutate(Start_Date = as.Date(
    Start_Date, format = "%Y-%m-%d"), 
    End_Date = as.Date(End_Date, format = "%Y-%m-%d" )) %>% 
  
  group_by(Medium, Vendor) %>% 
  summarise(
    Clicks = sum(Clicks), 
    Impressions = sum(Impressions), 
    Bounces = sum(Bounces), 
    Sessions = sum(Sessions), 
    UPV = sum(UPV),
    Views = sum(Views),
    Completions = sum(Completions),
    Step1 = sum(Step1),
    ClickRatePct = round(Clicks/Impressions * 100, 2),
    BounceRatePct = round(Bounces/Sessions * 100, 2),
    ViewRate = round(Views/Impressions * 100, 2),
    VTR = round(Completions/Impressions *100, 2),
    Cost = sum(Cost),
    Start_Date_New = min(Start_Date),
    End_Date_New = max(End_Date)
  ) %>% 
  mutate(ClickThruRate = paste0(ClickRatePct, "%"),
         BounceRate = paste0(BounceRatePct, "%"),
         Impressions = format(as.numeric(Impressions), big.mark=","), 
         UPV = format(as.numeric(UPV),  big.mark="," ),
         Cost = paste0("$ ", Cost),
         Av_TOP = round_hms(as_hms(Step1), 5), 
         Start_Date = format(as.Date(Start_Date_New), "%m-%Y"), 
         End_Date = format(as.Date(End_Date_New), "%m-%Y"), 
         End_Date = ifelse(End_Date == format(Sys.Date(),"%m-%Y"), "Ongoing", End_Date)) %>% 
  select(
    Medium, 
    Vendor, 
    Impressions, 
    ClickThruRate, 
    UPV, 
    BounceRate, 
    Av_TOP, 
    Cost,
    Start_Date, 
    End_Date
  )
  
```


```{r}
# NewData2 <- NewData %>% 
#   group_by(Medium, Vendor)
```

### Brief Description:

The FY20 advertising campaign targeting working adults (WA) has been multiphasic; part III started midway through the 3rd quarter. The Q3 portfolio consists mainly of Programmatic and Facebook display and LinkedIn and Gmail Inbox; a small amount goes to Facebook video.The new ad creative landing pages were rolled out on February 18,2020. Transition from /here to /excel has been seamless. 

It is difficult to speculate as to how Covid-19 may have impacted  performance, nevertheless, it is important to note that the social distancing due to the global pandemic became mandatory for the entire third month of the quarter. Digital and social media platforms remain a primary means of staying connected.

### Findings

```{r}
NewDataFY19Q3 <- NewDataFY20 %>%  select(Medium:End_Date) %>% arrange(Medium, Vendor)
#NewDataFY19Q3 <- NewDataFY19Q3[,c(4:13)]
landscape(knitr::kable(NewDataFY19Q3, "latex", caption = "FY20 Q3 Campaign Review: Working Adults", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 3) %>%
  pack_rows("Text", 4, 5) %>%
  pack_rows("Video", 6, 7)
  
```

```{r}
NewDataFY19 <-  NewData %>% filter(Quarter == "FY19Q3" & str_detect(AdSet, "WA")) %>%  
  separate(Vendor, c("Vendor", "Medium")) %>% 
  mutate(Start_Date = as.Date(
    Start_Date, format = "%Y-%m-%d"), 
    End_Date = as.Date(End_Date, format = "%Y-%m-%d" )) %>% 
  
  group_by(Medium, Vendor) %>% 
  summarise(
    Clicks = sum(Clicks), 
    Impressions = sum(Impressions), 
    Bounces = sum(Bounces), 
    Sessions = sum(Sessions), 
    UPV = sum(UPV),
    Views = sum(Views),
    Completions = sum(Completions),
    Step1 = sum(Step1),
    ClickRatePct = round(Clicks/Impressions * 100, 2),
    BounceRatePct = round(Bounces/Sessions * 100, 2),
    ViewRate = round(Views/Impressions * 100, 2),
    VTR = round(Completions/Impressions *100, 2),
    Cost = sum(Cost),
    Start_Date_New = min(Start_Date),
    End_Date_New = max(End_Date)
  ) %>% 
  mutate(ClickThruRate = paste0(ClickRatePct, "%"),
         BounceRate = paste0(BounceRatePct, "%"),
         Impressions = format(as.numeric(Impressions), big.mark=","), 
         UPV = format(as.numeric(UPV),  big.mark="," ),
         Cost = paste0("$ ", Cost),
         Av_TOP = round_hms(as_hms(Step1), 5), 
         Start_Date = format(as.Date(Start_Date_New), "%m-%Y"), 
         End_Date = format(as.Date(End_Date_New), "%m-%Y"), 
         End_Date = ifelse(End_Date == format(Sys.Date(),"%m-%Y"), "Ongoing", End_Date)) %>% 
  select(
    Medium, 
    Vendor, 
    Impressions, 
    ClickThruRate, 
    UPV, 
    BounceRate, 
    Av_TOP, 
    Cost,
    Start_Date, 
    End_Date
  )
  
```


```{r}
# NewData2 <- NewData %>% 
#   group_by(Medium, Vendor)
```



```{r eval=FALSE, include=FALSE}
NewDataFY19Q3 <- NewDataFY19 %>%  select(Medium:End_Date) %>% arrange(Medium, Vendor)
#NewDataFY19Q3 <- NewDataFY19Q3[,c(4:13)]
landscape(knitr::kable(NewDataFY19Q3, "latex", caption = "FY19 Q3 Campaign Targeting Working Adults", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Display", 1, 3) %>%
  pack_rows("Text", 4, 6)
  
```

```{r}
Forms <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/ThankYouFormCompletions.csv", header = T, stringsAsFactors = F)



DCForms <- Forms %>% filter(str_detect(Initial.Referral.Source,"DC")) %>% 
  mutate(Date = as.Date(Initial.Source.Date, format = "%m/%d/%Y"),
         LandingPage = 
           ifelse(Date <= "2019-08-01","/everyone",
                  ifelse(Date > "2019-08-01" & Date < "2020-02-18", "/here", "/excel")),
         FY = ifelse(Date < "2019-07-01", "FY19","FY20"), 
         Quarter = paste0((FY),"Q",quarter(Date, with_year = FALSE, fiscal_start = 7))
    
  ) %>% select(FY, Quarter,Date, everything())

DCForms <- DCForms %>% filter(str_detect(Initial.Referral.Source, "DC"), str_detect(Quarter, "3"))
kable(DCForms %>%  
        group_by(FY, Quarter, LandingPage) %>% 
        summarise(`Total Inquiries this Quarter` = n()))
```



* At the beginning of February, Phase 3 of the campaign targeting working adults launched and overall we see strong performance, particularly in the amount of ad driven traffic to the landing page.

* __DoubleClick Display:__ CTR, though averaging slightly lower than we have become accustomed to seeing this year, is still acceptable. Furthermore, this platform is driving a lot of traffic to the landing page, with a 75% bounce rate. The Spring creative has a slightly lower CTR than that of the Fall, however it has brought in more traffic with a lower bounce rate. 

* __Facebook Display:__ Although the CTR has continued to \textcolor{red}{trend downward}, Facebook display ads have, like DBM, been driving a lot of traffic this quarter. The bounce rate is comparable to last quarters, at 89%.

* __Gmail InBox:__ Open rates are above benchmark. Click to open rates, (CTOR), remain about 1.5%; while this is lower that the national industry average, they are no lower than we have seen in our other Gmail campaigns.

* __LinkedIn Inbox:__ Open rates continue to grow and are above benchmark.

* __Facebook Video:__ There is a small budget for this platform and, while we do not have benchmarks, both View Rates and View-thru-Rates are higher than we say FY20Q1.

* __Inquiries:__ Form completions are \textcolor{red}{down by one from FY19 Q3} as displayed above. More inquiry forms were completed during the /excel campaign.

* It looks as though we had started to run Instagram display and video ads, then \textcolor{red}{decided against it}. I will discuss this with Rinck.

* On the next page, I have provided a table to show the breakdown between the Fall and Spring creative.


```{r}
NewData1 <- read.csv("C:/Users/christine.iyer/Box/quarterly-ad-analytics-projects/FlowchartWorkingAdult.csv", header = T, stringsAsFactors = F)
```

```{r}
NewDataFY19Q3 <- NewData1 %>%
  filter(
    Quarter == "FY20Q3" & str_detect(AdSet, "WA")) %>%
  mutate(
    Vendor = str_sub(AdSet, 12, 14),
    Vendor = ifelse(str_detect(Vendor, "_"), str_sub(Vendor, 1,2), Vendor),
    Medium = str_sub(AdSet, 15,18),
    Medium = ifelse(str_detect(Medium, "DIS"), "Display", ifelse(str_detect(Medium, "VI"), "Video", "Story"))) %>% select(Medium,Vendor,  Impressions, CTR, UPV, BR, Av_TOP, Cost, Start_Date, End_Date) %>% arrange(Medium, Vendor)
```


```{r}

NewDataFY19Q3 <- NewDataFY19Q3[c(1,2,5,6),c(1:9)]
landscape(knitr::kable(NewDataFY19Q3, "latex", caption = "FY20 Q3 Campaign Trargeting Working Adults", booktabs = T))%>%
kable_styling(full_width = T)  %>%
  row_spec(0, angle = -45) %>%
  pack_rows("Programmatic Display", 1, 2) %>%
  pack_rows("Gmail Inbox", 3,4) 
```
